---
title: "Linear_non_linear_project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##lOADING ALL THE PACKAGES
```{r}
rm(list=ls(all=TRUE))

library(glmnet)
library(caret)
library(MASS)
library(vegan)
library(data.table)
library(doParallel)
library(DMwR)
library(dummies)
library(e1071)
library(standardize)
library(ggplot2)
library(arules)
```

## Reading the various datasets

```{r }
setwd("~/Linear and Non Linear/Data")
one=read.csv("Train.csv",na.strings=c("","NA"))
two=read.csv("Train_Claim.csv",na.strings=c("","NA"))
three=read.csv("Train_Demographics.csv",na.strings=c("","NA"))
four=read.csv("Train_Policy.csv",na.strings=c("","NA"))
five=read.csv("Train_Vehicle.csv")
```

```{r}
#Converting all the missing values to NA

#for Data of VEhicle
five$VehicleAttributeDetails=as.factor(ifelse(five$VehicleAttributeDetails=="???",NA,five$VehicleAttributeDetails))

#for Claim INformation
two$TypeOfCollission=as.factor(ifelse(two$TypeOfCollission=="?",NA,two$TypeOfCollission))
two$IncidentTime=as.factor(ifelse(two$IncidentTime=="-5",NA,two$IncidentTime))
two$PropertyDamage=as.factor(ifelse(two$PropertyDamage=="?",NA,two$PropertyDamage))
two$Witnesses=as.factor(ifelse(two$Witnesses=="MISSINGVALUE",NA,two$Witnesses))
two$PoliceReport=as.factor(ifelse(two$PoliceReport=="?",NA,two$PoliceReport))
two$AmountOfTotalClaim=(ifelse(two$AmountOfTotalClaim=="MISSEDDATA",NA,two$AmountOfTotalClaim))

#for policy  INFORMATIOn
four$PolicyAnnualPremium=(ifelse(four$PolicyAnnualPremium=="-1",NA,four$PolicyAnnualPremium))
```

```{r}
colSums(is.na(five))
colSums(is.na(two))
colSums(is.na(four))
colSums(is.na(three))
```



### Vehicle table has its attribute in a the vertical format, so connverting it into the horizontal format
```{r}
five_one=five[five$VehicleAttribute %in% c("VehicleID"),]
five_one$VehicleAttributeDetails=as.factor(as.character(five_one$VehicleAttributeDetails))
five_one=five_one[,-2]
str(five_one)       # we can delete Five_one i.e VEHICLE ID as iT OBVIOUSLY HAS all different factors

five_two=five[five$VehicleAttribute %in% c("VehicleMake"),] 
five_two$VehicleAttributeDetails2=as.factor(as.character(five_two$VehicleAttributeDetails))
str(five_two)
five_two=five_two[,c(-2,-3)]
five_three=five[five$VehicleAttribute %in% c("VehicleModel"),] 
five_three$VehicleAttributeDetails3=as.factor(as.character(five_three$VehicleAttributeDetails))
five_three=five_three[,c(-2,-3)]
five_four=five[five$VehicleAttribute %in% c("VehicleYOM"),]
five_four$VehicleAttributeDetails4=as.factor(as.character(five_four$VehicleAttributeDetails))
five_four=five_four[,c(-2,-3)]
str(five_four)
```


#merging all the csv files
```{r}
merge1 <- merge(five_three,five_two,by="CustomerID")
merge2 <- merge(merge1,five_four,by="CustomerID")
merge3 <- merge(merge2,four,by="CustomerID")
merge4 <- merge(merge3,three,by="CustomerID")
total <- merge(merge4,two,by="CustomerID")
total$InsurancePolicyNumber=as.factor(total$InsurancePolicyNumber)
#deleting customer ID and insurance policy number 
total=total[,setdiff(names(total),c("InsurancePolicyNumber","Country","AmountOfPropertyClaim_disc","AmountOfTotalClaim_disc","AmountOfInjuryClaim_disc"))]
total$InsuredZipCode=as.factor(as.integer(total$InsuredZipCode/1000))
str(total)
```

```{r}
#trying to fill NA's of insured gender using insured relationship
total$InsuredGender=as.factor(ifelse(total$InsuredRelationship=="wife","2",total$InsuredGender))
total$InsuredGender=as.factor(ifelse(total$InsuredRelationship=="husband","1",total$InsuredGender))

#Central imputation on the enitre dataset
finaldata=centralImputation(total)
```

###feature engineering
```{r}
#finding the number of days incident happened before accident
finaldata$DateOfIncident=as.Date(finaldata$DateOfIncident, format = "%Y-%m-%d")
finaldata$DateOfPolicyCoverage=as.Date(finaldata$DateOfPolicyCoverage, format = "%Y-%m-%d")
finaldata$incident_coverage=as.integer(finaldata$DateOfIncident-finaldata$DateOfPolicyCoverage)
finaldata$daysremainingforinsurance=finaldata$InsuredAge*365-finaldata$incident_coverage
final <- merge(one,finaldata,by="CustomerID")
final=final[,-1]
str(final)
```

#Distribution of y variable
```{r}
table(final$ReportedFraud)

```

###Checking for correlation between the numeric variables

```{r}
nums <- unlist(lapply(final, is.numeric))  
numeric_data = final[,nums]
cor = round(cor(numeric_data),1)
cor[upper.tri(cor)] = " "
cat("Correlation Plot\n")
cor

```


###Visualization


### Density plot for numeric variables
###Visualizing all the variables V/s the target variable
```{r}

for(i in 1:14){
  par(mfrow=c(2,2))
  print(ggplot(cbind(numeric_data,final$ReportedFraud), aes_string(x = colnames(numeric_data)[i], fill = "final$ReportedFraud")) +
          geom_density(alpha = 0.5) + 
          labs(title = colnames(numeric_data)[i], 
               x = paste("x",i,sep=""), 
               y = "Density", 
               col = "ReportedFraud"))
}

```

#### Binned variables V/s target
```{r}
library(scorecard)
data = final[,setdiff(names(final),c("InsuredZipCode","IncidentAddress","AmountOfTotalClaim"))]
woe_bins = scorecard::woebin(data, y="ReportedFraud", method="tree",positive = "Y",bin_num_limit = 4)
data_binned = scorecard::woebin_ply(data,woe_bins)  
plots_demog=scorecard::woebin_plot(woe_bins, x = NULL, title = NULL, show_iv = TRUE)
par(mfrow=c(2,2))
plots_demog
```

### Train Test split
```{r}
set.seed(1234)
final$ReportedFraud = as.factor(final$ReportedFraud)
Train_ID=caret::createDataPartition(final$ReportedFraud,p=0.8,list = F)
Train_data = final[Train_ID,]
Test_data = final[-Train_ID,]
Train_data_binned = data[Train_ID,]
Test_data_binned = data[-Train_ID,]
```

```{r}
library(h2o)
h2o.init()
finaldata.h2o=as.h2o(Train_data)
finaltest.h2o=as.h2o(Test_data)
y.dep<-1
x.indep<-2:40
```

```{r}
xgboost.model = h2o.xgboost(x = x.indep,
                           y = y.dep,
                           training_frame = finaldata.h2o,
                           validation_frame = finaltest.h2o,
                           booster = "gbtree",
                           seed = 1234,
                           nfolds = 5,
                           distribution="bernoulli",
                           eta = 0.151,
                           max_depth = 10,
                           sample_rate = 1,
                           col_sample_rate=1)
h2o.auc(h2o.performance(xgboost.model))
perf <- h2o.performance(xgboost.model, finaltest.h2o)
perf

```

```{r}
h2o.varimp(xgboost.model)
```

```{r}
glm.model <- h2o.glm(y=y.dep, x=x.indep, training_frame = finaldata.h2o, family = "binomial",nfolds=5)
h2o.auc(h2o.performance(glm.model))
#predict.dl2 <- as.data.frame(h2o.predict(gbm.model, finaltest.h2o))
perf <- h2o.performance(glm.model, finaltest.h2o)
perf
```